Lattice Boltzmann study of mass transfer for complicated geometries

### 2011-11-08 Text/introduction.tex
Need to do benchmarking.

\begin{document}
\section{Mass transfer definitions}
By the definition the mass transfer coefficient is the following:
\beq
k_L=\frac{\dot{m}}{P \Delta C},
\feq
where $\dot{m}$ is the mass rate $\Bigl[\frac{kg}{s}\Bigr]$, $P$ is the area of the surface
$\Bigl[m^2\Bigr]$, $\Delta C$ is the concentration difference $\Bigl[\frac{kg}{m^3}\Bigr]$.
Therefore, $k_L$ has a dimension of velocity $\Bigl[\frac{m}{s}\Bigr]$.

@@

\section{Improving velocity}

\section{Tweaking velocity}
This section does the job of increasing velocity results. The ulimate goal is to increase velocity
to about $20-50$ times for velocity while keeping dimensionless parameters the same. The
nondimensional parameter Peclet number governs the advection-diffusion equation:
\beq
Pe=\frac{U_{\bubble} N_y}{D},
\feq
where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
means one needs to increase the diffusion coefficient as well. We make a few runs with velocities
$5,10,20,40$ times larger than original velocities.

>>>>

\title{Lattice Boltzmann study of mass transfer for complicated geometries}

\begin{document}
\maketitle
\section{Mass transfer definitions}
By the definition the mass transfer coefficient is the following:
\beq
k_L=\frac{\dot{m}}{P \Delta C},
\feq
where $\dot{m}$ is the mass rate $\Bigl[\frac{kg}{s}\Bigr]$, $P$ is the area of the surface
$\Bigl[m^2\Bigr]$, $\Delta C$ is the concentration difference $\Bigl[\frac{kg}{m^3}\Bigr]$.
Therefore, $k_L$ has a dimension of velocity $\Bigl[\frac{m}{s}\Bigr]$.

@@

\section{Lattice Boltzmann Benchmarks}
\citet{vanbaten-circular} represented a bubble with two hemisperes and a thin film. We want to
perform the benchmarking against these two representative cases.

\subsection{The radial case}
We want to examine the bounce-back conditions against the analytical solution. The system can be
prescribed by the following system of equations:
\beq
\begin{aligned}
&\partial_t C(r,t)=\frac{1}{r}\partial_r r \partial_r C(r,t)\\
&C(a,t)=C_0,\,C(r,0)=C_{init}
\end{aligned}
\feq 
The solution is represented as \cite{chemical-correlations}:
\beq
\frac{C(r,t)-C_{0}}{C_{init}-C_{0})}=\sum_{n=1}^{\infty}{\frac{2}{\mu_n
J_1(\mu_n)}\exp\Bigl(-\mu_n^2 \frac{D t}{a^2} \Bigr)J_0(\mu_n \frac{r}{a})},
\feq
where $\mu_n$ is the $n$-th zero root of the $0$th order Bessel polynomial $J_0(\mu_n)=0$. Some of
the corresponding roots are as follows: $\mu_1=2.4048$,$\mu_2=5.5201$,$\mu_3=8.6537$,
$\mu_4=11.7915$,$\mu_5=14.9309$.
By taking initial concentration to be $0$, one can obtain the following solution:
\beq
C(r,t)=C_0 \Biggl(1 - \sum_{n=1}^{\infty}{\frac{2}{\mu_n
J_1(\mu_n)}\exp\Bigl(-\mu_n^2 \frac{D t}{a^2} \Bigr)J_0(\mu_n \frac{r}{a})}\Biggr).
\feq

Here some

\section{Tweaking velocity}
This section does the job of increasing velocity results. The ulimate goal is to increase velocity
to about $20-50$ times for velocity while keeping dimensionless parameters the same. The
nondimensional parameter Peclet number governs the advection-diffusion equation:
\beq
Pe=\frac{U_{bubble} N_y}{D},
\feq
where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
means one needs to increase the diffusion coefficient as well. We make a few runs with velocities
$5,10,20,40$ times larger than original velocities.
